Symmetric Circuits for Rank Gates

### 2018-03-01 sections/symmetric-circuits.tex
A complete draft minus the conclusion. Large changes made to a number of sections.

Anderson and Dawar's argument makes use of the fact that many important circuit
properties are polynomial-time decidable for circuits defined over symmetric
bases. While we should like to construct an analogous argument, we show in
Section~\ref{sec:transparency-and-unique-extension} that for circuits that
include gates computing non-symmetric functions most of these important circuit
properties are at least as hard to decide as the graph-isomorphism problem. As
such, constructing an analogous translation, as well as establishing the
numerous other needed results whose proofs rely on certain properties being
polynomial-time decidable, would be non-trivial.

In order to proceed we will restrict ourselves to circuits with certain
constraints on how those gates computing non-symmetric functions can be wired
into the circuit. We call these circuits \emph{transparent} circuits. We show in
Sections~\ref{sec:transparency-and-unique-extensions} that transparency is
sufficient to allow for the polynomial-time decidability of many important
circuit properties, while still keeping the circuit model powerful enough for us
to establish a translation from formulas to families of circuits.

@@

We note that the construction of $C'$ from $C$ in
Lemma~\ref{lem:redundant-gates} can be implemented so as to run in time
polynomial in the size of $C$. As such, for the remainder of this paper we
assume, unless stated otherwise, every circuit has no redundant gates. With this
assumption in mind we now show that every circuit with unique children (and so
unique labels) has unique extensions.

@@

It follows from Proposition~\ref{prop:unique-children-unique-extensions} that if
$C$ is of order $n$ then for each $\sigma \in \sym_n$ there exists at most one
$\pi_\sigma \in \aut(C)$ extending $\sigma$. However, if $g$ is a gate in $C$
and $\pi_{\sigma} g = g'$ there may no `canonical' $\lambda \in \aut(g)$
witnessing the isomorphism-equivalence, i.e.\ such that $\pi L(g) = L(g')
\lambda$. It is this lack of a `canonical' choice that allows us to prove in
Section~\ref{sec:transparency-and-unique-extensions} that a great many important
circuit properties (e.g. the orbit of a gate, symmetry of a circuit, etc.) for
circuits with unique gates are at least as hard as the graph-isomorphism problem
to decide.

In contrast, it is easy to see that if $C$ has unique labels, and $g$ and $g'$
are gates in the circuit, then $L(g)$ and $L(g')$ are isomorphism-equivalent if,
and only if, $\lambda := L(g')^{-1}L(g)$ is in $\aut(g)$. We show in
Section~\ref{sec:transparency-and-unique-extensions} all of the circuit
properties of interest in this paper are polynomial-time decidable for circuits
with unique labels. Moreover, we show in
Proposition~\ref{prop:transparent-unique} that a transparent circuit can be
converted into an equivalent circuit with unique labels in time polynomial in
the size of the circuit. Since we are working with $P$-uniform families of
transparent circuits, this fact allows us to assume, without a loss of
generality, that transparent circuits have unique labels (and, from
\ref{prop:unique-children-unique-extensions} so unique extensions).

@@

\begin{proof}
  From $C_n$ we construct $C_n'$ as follows. For each gate $g \in C_n$ labelled
  by a member of $\mathbb{B}$ we have a symmetric circuit $C_g$ from
  Proposition~\ref{prop:function-maj} that computes the same function as $g$.
  Then let $C_n'$ be as $C_n$ but with each gate $g \in C_n$ replaced by $C_g$.
  It is easy to see that $C_n'$ is symmetric. We also have that each gate $g$
  must have at most $\vert C_n \vert$ inputs, and so the size of $C_g$ is
  bounded by $5 \vert C_n \vert + 3$. Thus the size of $C_n'$ is bounded by
  $(5f(n)+3) f(n)$. This algorithm clearly runs in polynomial-time.
\end{proof}

This result gives us that for any family of circuits over an arbitrary basis of
symmetric functions we can construct another symmetric circuit family computing
the same function over the majority basis without a blowup in size. Moreover, we
also have that if the first family was uniform the second family will be as
well. As such, we cannot extend the power of the $P$-uniform symmetric circuits
families studied by Anderson and Dawar \cite{AndersonD17} by simply considering
alternative bases of symmetric functions, thus motivating the generalisation
developed in the previous subsection to non-symmetric functions.
\end{document}

>>>>

Anderson and Dawar's argument makes use of the fact that many important circuit
properties are polynomial-time decidable for circuits defined over symmetric
bases. While we should like to construct an analogous argument, we show in
Section~\ref{sec:transparent} that for circuits that include gates computing
non-symmetric functions most of these important circuit properties are at least
as hard to decide as the graph-isomorphism problem. As such, constructing an
analogous translation, as well as establishing the numerous other needed results
whose proofs rely on certain properties being polynomial-time decidable, would
be non-trivial.

In order to proceed we will restrict ourselves to circuits with certain
constraints on how those gates computing non-symmetric functions can be wired
into the circuit. We call these circuits \emph{transparent} circuits. We show in
Sections~\ref{sec:transparent} that transparency is sufficient to allow for the
polynomial-time decidability of many important circuit properties, while still
keeping the circuit model powerful enough for us to establish a translation from
formulas to families of circuits.

@@

We note that the construction of $C'$ from $C$ in
Lemma~\ref{lem:redundant-gates} can be implemented by an algorithm that runs in
time polynomial in the size of $C$. As such, for the remainder of this paper we
assume, unless stated otherwise, every circuit has no redundant gates. With this
assumption in mind we now show that every circuit with unique children (and so
unique labels) has unique extensions.

@@

It follows from Proposition~\ref{prop:unique-children-unique-extensions} that if
$C$ is of order $n$ then for each $\sigma \in \sym_n$ there exists at most one
$\pi_\sigma \in \aut(C)$ extending $\sigma$. This means that if $C$ is symmetric
for each $\sigma \in \sym_n$ there is always a canonical automorphism
$\pi_\sigma$ extending $\sigma$. However, for a gate $g$ in $C$ there may no
canonical $\lambda \in \aut(g)$ witnessing the validity of the mapping from $g$
to $\pi_\sigma g$, i.e.\ such that $\pi L(g) = L(g') \lambda$. We prove in
Section~\ref{sec:transparent} that in fact, for the class of circuits with
unique children, deciding if there is an isomorphism-equivalence between two
gates is as hard as the graph-isomorphism problem. It follows that a great many
important circuit properties (e.g. the orbit of a gate, symmetry of a circuit,
etc.) for circuits with unique gates are at the very least not obviously
polynomial-time decidable.

In contrast, it is easy to see that if $C$ has unique labels, and $g$ and $g'$
are gates in the circuit $C$, then $L(g)$ and $L(g')$ are isomorphism-equivalent
if, and only if, $\lambda := L(g')^{-1}L(g)$ is in $\aut(g)$. In this case,
rather than having to decide the isomorphism problem we simply need to check if a given
candidate is in fact a valid isomorphism. We prove in
Section~\ref{sec:transparent} that all of the circuit properties of interest in
this paper are polynomial-time decidable for circuits with unique labels.
Moreover, we show in Lemma~\ref{lem:transparent-unique} that a
transparent circuit can be converted into an equivalent circuit with unique
labels in time polynomial in the size of the circuit. Since we are working with
$P$-uniform families of transparent circuits, this fact allows us to assume,
without a loss of generality, that transparent circuits have unique labels (and,
from \ref{prop:unique-children-unique-extensions} so unique extensions).

@@

\begin{proof}
  From $C_n$ we construct $C_n'$ as follows. For each gate $g \in C_n$ labelled
  by a member of $\mathbb{B}$ we have a symmetric circuit $C_g$ from
  Proposition~\ref{prop:fuctions-maj} that computes the same function as $g$.
  Then let $C_n'$ be as $C_n$ but with each gate $g \in C_n$ replaced by $C_g$.
  It is easy to see that $C_n'$ is symmetric. We also have that each gate $g$
  must have at most $\vert C_n \vert$ inputs, and so the size of $C_g$ is
  bounded by $5 \vert C_n \vert + 3$. Thus the size of $C_n'$ is bounded by
  $(5f(n)+3) f(n)$. This algorithm clearly runs in polynomial-time.
\end{proof}

This result gives us that for any family of circuits over an arbitrary basis of
symmetric functions we can construct another symmetric circuit family computing
the same function over the majority basis without a blowup in size. Moreover, we
also have that if the first family was uniform the second family will be as
well. As such, we cannot extend the power of the $P$-uniform symmetric circuits
families studied by Anderson and Dawar~\cite{AndersonD17} by simply considering
alternative bases of symmetric functions, thus motivating the generalisation
developed in the previous subsection to non-symmetric functions.
\end{document}

### 2018-03-01 sections/transparency-and-unique-extensions.tex
A complete draft minus the conclusion. Large changes made to a number of sections.

\begin{lem}
  Let $C := \langle G, \Omega, \Sigma, \Lambda, L\rangle$ be a $(\BB,
  \rho)$-circuit of order $n$ and $C_{\equiv} = \langle G_\equiv ,
  \Omega_\equiv, \Sigma_\equiv , \Lambda_\equiv, L_\equiv \rangle$ be a quotient
  of $C$. Then $C$ and $C_{\equiv}$ compute the same function and each
  syntacitic-equivalence class in $C_\equiv$ is a singleton. Moreover, if $C$ is
  symmetric then $C_{\equiv}$ is symmetric, and for all $g \in G$, $g$ has
  unique labels in $C$ if, and only if, $[g]$ has unique labels in $C_{\equiv}$.
  \label{lem:quotient-circuits-preserve}
\end{lem}
\begin{proof}
  We first prove that $C_\equiv$ and $C$ compute the same function. Let
  $\mathcal{A}$ be a $\rho$-structure of size $n$ and let $\gamma$ be a
  bijection from $U$ to $[n]$. We now show that for all $g \in G$, $C_\equiv
  [\gamma \mathcal{A}]([g]) = C[\gamma \mathcal{A}](g)$. We do this by induction
  on the depth of a gate. Suppose $g \in G$ has depth $0$. In this case $g$ is
  an input gate and the result follows trivially. Suppose $g$ is an internal
  gate and suppose for all $h$ of depth less than $g$ we have that
  $C_\equiv[\gamma \mathcal{A}]([h]) = C[\gamma \mathcal{A}](h)$. We have that
  there exists $g' \in [g]$ such that $L_\equiv ([g]) = L(g') /_\equiv$ and
  $\Sigma_\equiv([g]) = \Sigma (g) = \Sigma (g')$. We have from Lemma~\ref{} and
  the inductive hypothesis that there exists $\lambda \in \aut(g)$ such that
  $L_\equiv ([g]) = L(g') = L(g) \lambda$. It follows from the fact that
  $\Sigma(g)$ is a structured function that $C_\equiv[\gamma \mathcal{A}]([g]) =
  \Sigma_\equiv ([g])(L^{\gamma \mathcal{A}}_\equiv([g])) = \Sigma (g')
  (L^{\gamma \mathcal{A}}(g')) = \Sigma (g)(L^{\gamma \mathcal{A}}(g) \lambda) =
  \Sigma (g) (L^{\gamma \mathcal{A}}(g)) = C[\gamma \mathcal{A}](g)$.

@@

We now show that transparent circuits can be transformed in polynomial time into
equivalent circuit with unique labels, and hence unique extensions (see
Lemma~\ref{}), and that this transformation preserves important properties of
the circuit.

@@

We now show that it is possible to compute the action of $\sym_n$ on the gates
of a circuit of order $n$ with unique labels in polynomial time. Recall that
from Proposition~\ref{prop:transparent-unique} we may, without a loss of
generality, restrict our attention from transparent circuits to circuits with
unique labels. The proof technique used here is similar to the one used by
Anderson and Dawar~\cite{AndersonD17}.

@@

  Let $h$ be any gate in the circuit. Suppose $h$ is an input gate. If $h$ is a
  constant gate then let $\pi (h) = h'$. If $h$ is a relational gate such that
  $R := \Sigma(h)$, then check if there exists $h'$ such that $\Sigma (h') = R$,
  $\sigma \Lambda_R(h) = \Lambda_R(h')$, and either both $h$ and $h'$ are output
  gates or neither are. If no such $h'$ exists then halt and output that no
  automorphism exists. If both $h$ and $h'$ are not output gates then set $\pi
  (h) = h'$. If both are output gates then check if $\sigma \Omega^{-1}(h) =
  \Omega^{-1}(h')$. If equality holds set $\pi(h) = h'$, otherwise halt and
  output that no automorphism exists. We have from Lemma~\ref{} that there is at
  most one gate $h'$ that meets the above criteria, and so $\pi(h)$ is well
  defined.

@@

Anderson and Dawar~\cite{AndersonD17}, in their study of circuits with symmetric
gates, show that such circuits may be transformed in polynomial time into
equivalent circuits with unique extensions. They do this by showing that a
circuit with symmetric gates may be transformed into an equivalent \emph{rigid}
circuit in polynomial time, and that all rigid circuits have unique extensions.
Moreover, they also prove the existence of polynomial-time algorithms computing
the action of a permutation on a rigid circuit, and the orbits and coarsest
supporting partitions of gates in a rigid circuits. We have shown that
transparent circuits can be translated into equivalent circuits with unique
labels in polynomial time, and that circuits with unique labels have unique
extensions (see Proposition~\ref{}). Moreover, we have similarly shown that, for
transparent circuits, the action of a permutation, as well as the coarsest
supporting partition and orbit of a gate (or element of the universe of a gate),
can be computed in polynomial-time. Since all circuits with symmetric gates are
transparent, this is direct generalisation of the results of Anderson an Dawar.

@@

  Let $R$ be a relation symbol in $\rho$ and let $k := \arty(R) > 0$. Let $G_{R}
  := \{g_{R, \vec{c}} : \vec{c} \in [n]^k\}$, $G_{\text{mid}} := \{g_{\lor},
  g_{\land}, g_{\text{out}} \}$, $G_{\rank} : = \{ g^1_{\rank}, g^2_{\rank}\}$,
  and $G_{\text{nodes}} := \{g_{i, (u,v)} : i \in [2] \, (u,v) \in [a] \times
  [b] \}$. Let $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a
  $(\{\rank^{1}_2\}, \rho)$-circuit of order $n$ defined as follows. Let $G =
  G_R \cup G_{\text{mid}} \cup G_{\rank} \cup G_{\text{nodes}}$ and $\Omega$ be
  the $0$-ary function $\land_{\text{out}}$. For each $\vec{c} \in
  [n]^{\arty(R)}$ let $\Lambda_R(\vec{c}) = g_{R, \vec{c}}$. Define $\Sigma$ as
  follows. For each $g \in G$,
  \begin{itemize}
    \setlength\itemsep{0mm}
  \item if $g = \land_{\text{out}}$ then $\Sigma(g) = \land[2]$,
  \item if $g \in G_\rank$ then $\Sigma(g) = \rank^r_p [a,b]$,
  \item if $g \in G_{\text{nodes}}$ then $\Sigma(g) = \land[1]$,
  \item if $g = \land[n^k]$, $\Sigma (g) = \land[n^k]$ and if $g = g_{\lor}$
    then $\Sigma(g) = \lor[n^k]$, and
  \item if $g \in G_R$ then $\Sigma(g) = R$.
  \end{itemize}
  Define $L$ as follows. For each $g \in G$,
  \begin{itemize}
    \setlength\itemsep{0mm}
  \item if $g = \land_{\text{out}}$ then for each $i \in [2]$, $L(g)(i) :=
    g^i_{\rank}$,
  \item if $g \in G_\rank$ and $g = g^i_{\rank}$ then for all $(p,q) \in
    \ind(g)$, $L(g)(p,q) = g_{i, (p,q)}$,
  \item if $g \in G_{\text{nodes}}$ and $g = g_{i, (p,q)}$ then if $(p, q \in
    E_i)$ then $L(g)(1) = g_{\land}$, otherwise $L(g)(1) = g_\lor$, and
  \item if $g = g_\land$ or $g = g_\lor$ then for all $p \in [n^k]$ we have that
    $L(g)(p)$ equals $\Lambda^{-1}(\vec{c}_p)$, where $\vec{c}_p$ is the $p$th
    element of $[n]^k$ in the lexicographical ordering on $[n]^k$.
  \end{itemize}

@@

We recall that a circuit $C$ is transparent if, and only if, every non-symmetric
gate in $C$ has injective labels and unique children. We have shown that
computing the syntactic-equivalence relation is at least as hard as the
graph-isomorphism problem if we restrict ourselves to either the class of
circuits in which non-symmetric gates have injective labels
(Proposition~\ref{prop:syntactic-graph-iso}) or the class of circuits in which
each non-symmetric gate has unique children
(Lemma~\ref{lem:syntactic-equivalence-equivalence-unique-gates-hard}).

@@

We have from Propositions~\ref{prop:syntactic-graph-iso}
and~\ref{prop:graph-iso-symmetric}, and
Lemmas~\ref{lem:syntactically-equivalent-unique-labels},
\ref{lem:graph-iso-to-orbit}
and~\ref{lem:syntactically-equivilent-unique-extensions}, that a number of basic
circuit properties are at least as hard for general circuits as the
graph-isomorphism problem. In contrast, all of these properties are known to be
polynomial-time decidable for transparent circuits (as follows from
Lemmas~\ref{lem:unique-labels-syntactic-equiv}
and~\ref{lem:computing-support-orbit-gate}).

>>>>

\begin{lem}
  Let $C := \langle G, \Omega, \Sigma, \Lambda, L\rangle$ be a $(\BB,
  \rho)$-circuit of order $n$ and $C_{\equiv} = \langle G_\equiv ,
  \Omega_\equiv, \Sigma_\equiv , \Lambda_\equiv, L_\equiv \rangle$ be a quotient
  of $C$. Then $C$ and $C_{\equiv}$ compute the same function and each
  syntacitic-equivalence class in $C_\equiv$ is a singleton. Moreover, if $C$ is
  symmetric then $C_{\equiv}$ is symmetric, and for all $g \in G$, $g$ has
  unique labels in $C$ if, and only if, $[g]$ has unique labels in $C_{\equiv}$.
  \label{lem:quotient-circuits-preserve}
\end{lem}
\begin{proof}
  We first prove that $C_\equiv$ and $C$ compute the same function. Let
  $\mathcal{A}$ be a $\rho$-structure of size $n$ and let $\gamma$ be a
  bijection from $U$ to $[n]$. We now show that for all $g \in G$, $C_\equiv
  [\gamma \mathcal{A}]([g]) = C[\gamma \mathcal{A}](g)$. We do this by induction
  on the depth of a gate. Suppose $g \in G$ has depth $0$. In this case $g$ is
  an input gate and the result follows trivially. Suppose $g$ is an internal
  gate and suppose for all $h$ of depth less than $g$ we have that
  $C_\equiv[\gamma \mathcal{A}]([h]) = C[\gamma \mathcal{A}](h)$. We have that
  there exists $g' \in [g]$ such that $L_\equiv ([g]) = L(g') /_\equiv$ and
  $\Sigma_\equiv([g]) = \Sigma (g) = \Sigma (g')$. We have from
  Lemma~\ref{lem:syntactic-equivalence-equal-function} and the inductive
  hypothesis that there exists $\lambda \in \aut(g)$ such that $L_\equiv ([g]) =
  L(g') = L(g) \lambda$. It follows from the fact that $\Sigma(g)$ is a
  structured function that $C_\equiv[\gamma \mathcal{A}]([g]) = \Sigma_\equiv
  ([g])(L^{\gamma \mathcal{A}}_\equiv([g])) = \Sigma (g') (L^{\gamma
    \mathcal{A}}(g')) = \Sigma (g)(L^{\gamma \mathcal{A}}(g) \lambda) = \Sigma
  (g) (L^{\gamma \mathcal{A}}(g)) = C[\gamma \mathcal{A}](g)$.

@@

We now show that transparent circuits can be transformed in polynomial time into
equivalent circuit with unique labels, and hence unique extensions (see
Proposition~\ref{prop:unique-children-unique-extensions}), and that this transformation preserves important properties of
the circuit.

@@

We now show that it is possible to compute the action of $\sym_n$ on the gates
of a circuit of order $n$ with unique labels in polynomial time. Recall that
from Lemma~\ref{lem:transparent-unique} we may, without a loss of
generality, restrict our attention from transparent circuits to circuits with
unique labels. The proof technique used here is similar to the one used by
Anderson and Dawar~\cite{AndersonD17}.

@@

  Let $h$ be any gate in the circuit. Suppose $h$ is an input gate. If $h$ is a
  constant gate then let $\pi (h) = h'$. If $h$ is a relational gate such that
  $R := \Sigma(h)$, then check if there exists $h'$ such that $\Sigma (h') = R$,
  $\sigma \Lambda_R(h) = \Lambda_R(h')$, and either both $h$ and $h'$ are output
  gates or neither are. If no such $h'$ exists then halt and output that no
  automorphism exists. If both $h$ and $h'$ are not output gates then set $\pi
  (h) = h'$. If both are output gates then check if $\sigma \Omega^{-1}(h) =
  \Omega^{-1}(h')$. If equality holds set $\pi(h) = h'$, otherwise halt and
  output that no automorphism exists. We have from
  Proposition~\ref{prop:unique-children-unique-extensions} that there is at
  most one gate $h'$ that meets the above criteria, and so $\pi(h)$ is well
  defined.

@@

Anderson and Dawar~\cite{AndersonD17}, in their study of circuits with symmetric
gates, show that such circuits may be transformed in polynomial time into
equivalent circuits with unique extensions. They do this by showing that a
circuit with symmetric gates may be transformed into an equivalent \emph{rigid}
circuit in polynomial time, and that all rigid circuits have unique extensions.
Moreover, they also prove the existence of polynomial-time algorithms computing
the action of a permutation on a rigid circuit, and the orbits and coarsest
supporting partitions of gates in a rigid circuits. We have shown that
transparent circuits can be translated into equivalent circuits with unique
labels in polynomial time, and that circuits with unique labels have unique
extensions (see Proposition~\ref{prop:unique-children-unique-extensions}). Moreover, we have similarly shown that, for
transparent circuits, the action of a permutation, as well as the coarsest
supporting partition and orbit of a gate (or element of the universe of a gate),
can be computed in polynomial-time. Since all circuits with symmetric gates are
transparent, this is direct generalisation of the results of Anderson an Dawar.

@@

  Let $R$ be a relation symbol in $\rho$ and let $k := \arty(R) > 0$. Let $G_{R}
  := \{g_{R, \vec{c}} : \vec{c} \in [n]^k\}$, $G_{\text{mid}} := \{g_{\lor},
  g_{\land}, g_{\text{out}} \}$, $G_{\rank} : = \{ g^1_{\rank}, g^2_{\rank}\}$,
  and $G_{\text{nodes}} := \{g_{i, (u,v)} : i \in [2] \, (u,v) \in [a] \times
  [b] \}$. Let $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a
  $(\{\rank^{1}_2\}, \rho)$-circuit of order $n$ defined as follows. Let $G =
  G_R \cup G_{\text{mid}} \cup G_{\rank} \cup G_{\text{nodes}}$ and $\Omega$ be
  the $0$-ary function $\land_{\text{out}}$. For each $\vec{c} \in
  [n]^{\arty(R)}$ let $\Lambda_R(\vec{c}) = g_{R, \vec{c}}$. Define $\Sigma$ as
  follows. For each $g \in G$,
  \begin{itemizens}
    \setlength\itemsep{0mm}
  \item if $g = \land_{\text{out}}$ then $\Sigma(g) = \land[2]$,
  \item if $g \in G_\rank$ then $\Sigma(g) = \rank^r_p [a,b]$,
  \item if $g \in G_{\text{nodes}}$ then $\Sigma(g) = \land[1]$,
  \item if $g = \land[n^k]$, $\Sigma (g) = \land[n^k]$ and if $g = g_{\lor}$
    then $\Sigma(g) = \lor[n^k]$, and
  \item if $g \in G_R$ then $\Sigma(g) = R$.
  \end{itemizens}
  Define $L$ as follows. For each $g \in G$,
  \begin{itemizens}
    \setlength\itemsep{0mm}
  \item if $g = \land_{\text{out}}$ then for each $i \in [2]$, $L(g)(i) :=
    g^i_{\rank}$,
  \item if $g \in G_\rank$ and $g = g^i_{\rank}$ then for all $(p,q) \in
    \ind(g)$, $L(g)(p,q) = g_{i, (p,q)}$,
  \item if $g \in G_{\text{nodes}}$ and $g = g_{i, (p,q)}$ then if $(p, q \in
    E_i)$ then $L(g)(1) = g_{\land}$, otherwise $L(g)(1) = g_\lor$, and
  \item if $g = g_\land$ or $g = g_\lor$ then for all $p \in [n^k]$ we have that
    $L(g)(p)$ equals $\Lambda^{-1}(\vec{c}_p)$, where $\vec{c}_p$ is the $p$th
    element of $[n]^k$ in the lexicographical ordering on $[n]^k$.
  \end{itemizens}

@@

We recall that a circuit $C$ is transparent if, and only if, every non-symmetric
gate in $C$ has injective labels and unique children. We have shown that
computing the syntactic-equivalence relation is at least as hard as the
graph-isomorphism problem if we restrict ourselves to either the class of
circuits in which non-symmetric gates have injective labels
(Proposition~\ref{prop:syntactic-graph-iso}) or the class of circuits in which
each non-symmetric gate has unique children
(Lemma~\ref{lem:syntactic-equivalence-unique-gates-hard}).

@@

We have from Propositions~\ref{prop:syntactic-graph-iso}
and~\ref{prop:graph-iso-symmetric}, and
Lemmas~\ref{lem:syntactically-equivalent-unique-labels},
\ref{lem:graph-iso-to-orbit}
and~\ref{lem:syntactically-equivilent-unique-extensions}, that a number of basic
circuit properties are at least as hard for general circuits as the
graph-isomorphism problem. In contrast, all of these properties are known to be
polynomial-time decidable for transparent circuits (as follows from
Lemmas~\ref{lem:transparent-syntactic-equiv}
and~\ref{lem:computing-support-orbit-gate}).
